%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%------------------------------------------------
%	TITLE SECTION
%------------------------------------------------

\namesection{Eduardo}{Delgaldo}{
http://github.com/eddmt \\
eduardo.mathias@pm.me | Phone: +598 98 038 315
}

%------------------------------------------------
%	LEFT COLUMN
%------------------------------------------------


\begin{minipage}[t]{0.33\textwidth} 

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}
\subsection{Web Development}
\location{Strong knowledge on:}
PHP [WordPress]\textbullet{} Javascript [Angular, React] \textbullet{} HTML \textbullet{} CSS/SCSS \textbullet{} SQL \textbullet{} Git
\sectionsep

\location{Worked with:}
Ruby [Ruby On Rails] \textbullet{} Java [Apex/Salesforce, Selenium] \textbullet{} Python [Django]
\sectionsep

\location{Familiar with:}
VueJS \textbullet{} Typescript
\sectionsep

\subsection{Languages}
Spanish (Native) \textbullet{} English (Advanced) \textbullet{} Portuguese (Medium)
\sectionsep

%------------------------------------------------
% Interests
%------------------------------------------------

\section{Interests}

\subsection{Computer-related}

Linux Servers \textbullet{} Ethereum \textbullet{} Cryptocurrencies \textbullet{} Vim/Nvim \textbullet{} \LaTeX \textbullet{} Arduino

\sectionsep

\subsection{Miscellaneous}
Esperanto \& constructed languages \textbullet{} Accountancy \& Economy studies \textbullet{} Veganism \textbullet{} Writing

\sectionsep

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{UDELAR}
\descript{Facultad de Psicología}
\location{2013}
\sectionsep

\subsection{Universidad ORT}
\descript{Professinal update on PHP}
\location{2007}
\sectionsep

\subsection{UDELAR}
\descript{Facultad de Derecho}
\location{2006-2008}
\sectionsep

\subsection{Elbio Fernández}
\descript{Highschool}
\location{2000-2005}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth}

\vspace{\topsep}

{\Large I'm a web developer with 10 years of experience, Javascript, PHP, HTML \& CSS emphasized. I challenge myself to achieve excellence and commitment.}

\hrulefill

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Globant}
\descript{| Semi Senior Web Developer}

\location{Dec 2013 – Jan 2018}
\begin{tightemize}
\item I worked in several large scale projects with extensive use of Angular, Bower, Grunt and Jasmine/Mocha.
\item Among the projects I was involved in: Autodesk, Metromile and National Geographic.
\item All the projects demaned compliance with code standards, unit testing and high communication skills when working with remote teams. 
\item High degree of understanding of Git and branching best practices.
\end{tightemize}

\sectionsep

%------------------------------------------------

\runsubsection{Benoit}
\descript{| Security Analysis \& Software Engineering}

\location{Jan 2013 – Sep 2013}
\begin{tightemize}
\item I worked on several Ruby projects implementing Spree e-commerce platform and Refinery CMS.
\item Development required BackboneJs and Ruby On Rails.
\item Handled security reports and data analysis for private networks using OSSIM Alien Vault platform. It required Ruby scripting.
\end{tightemize}

\sectionsep

%------------------------------------------------

\runsubsection{Farm.co}
\descript{| Quality Assurance \& PHP Developer}

\location{Ago 2012 – Nov 2012}
\begin{tightemize}
\item Worked on the implementation of Jenkins and Behat servers. Among other testing tasks, I was in charge of developing testing processes.
\item PHP projects relied on Symfony and Doctrine frameworks and demanded strict code standards.
\end{tightemize}

\sectionsep

%------------------------------------------------

\runsubsection{Takeoff Media}
\descript{| WordPress Developer \& Advisor}

\location{Oct 2010 – Ago 2012}
\begin{tightemize}
\item I was in charge of refactoring and mantaining the DIRECTV Sports portal. This required theme and plugin development from scratch.
\item Created a WordPress plugin meant to synchronize 50+ blogs in a multi-site install, developed for Walmart network.
\item Worked on a PHP tool to keep track of tasks and resources in Jira and Basecamp, using Doctrine and Symfony
\end{tightemize}

\sectionsep

%------------------------------------------------

\runsubsection{Ledon West}
\descript{| Frontend Developer}

\location{May 2010 – Oct 2010}
\begin{tightemize}
\item Took part in the restructuring of Startups.com, based on PHP/Codeigniter. The job required shell scripting as well.
\item In the phase that followed, I worked on the migration to OSQA, a platform developed with Django.
\end{tightemize}

\sectionsep

%------------------------------------------------

\runsubsection{Timba}
\descript{| Quality Assurance \& Salesforce Developer}

\location{Jul 2008 – Jan 2010}
\begin{tightemize}
\item Developed for several projects for the Salesforce platform.
\item Worked on automated testing based on Selenium and Java.
\item Regulary unit testing and writing of QA documentation.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
